V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints for a Previous Single Transit Event of V1298~Tau~e

### 2021-11-01 src/ms.tex
last paragraph changes

The second scenario is that the original single transit of \planete could have been filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations. \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data. The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and therefore are not resolved enough to be able to look for starspot crossings. However, the new \tess\ 20-second and 2-minute data may yield insight into if the anomaly at $t \sim 4648.8$~BKJD is an affect from a starspot crossing event, an overlapping transit of a currently unknown planet, or general noise in the data.

>>>>

The second scenario is that the original single transit of \planete could have been filled-in via spot-crossing events, making it appear shallower in the \textit{K2} observations. Young stars are known to have very high spot coverage, anywhere from 30-80\% \citep[][]{grankin99, gully17, feinstein20}. It is therefore likely the surface of \sname is dominated by stellar inhomogeneities. \cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data. The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and are likely not resolved enough to be able to look for starspot crossings. However, the new \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events. Our transit of \planete from the FFIs shows some structure, particularly with a slight increase in transit depth around $t \approx 4648.8$~BKJD. At the 10-minute cadence, it is hard to rule out noise as the source of this structure. However if there is such evidence of starspot crossings in the higher-cadence \tess\ observations, it would be interesting if any of the events dilutes the transit enough to result in a similar transit depth to that which was seen in \textit{K2}.
